\chapter{Outlook} \label{chap:outlook}
The developed method can segment the sciatic nerve with human-level performance regarding quantitative evaluation metrics. As we aim to leverage the diagnosis and the assessment of all peripheral nerves, obviously future work should go in the direction of a method which can segment all peripheral nerves. Although not used in this work, we have further \gls{mrn} images available from different anatomical regions (upper \& lower arm, lower leg) for the volunteer cohort. A method could be developed also incorporating these \gls{mrn} images. However, given that the sciatic nerve is the largest nerve in the human body, segmenting smaller peripheral nerves might be difficult. Almost certainly a large number of \gls{mrn} images with higher resolution would be required to achieve an acceptable level of segmentation performance. Once peripheral nerves can robustly be segmented, potentially new biomarkers, such as texture analysis-based biomarkers~\cite{FelisazTextureNeuropathy}, could be extracted from the high-resolution \gls{mrn} images and used for assessment and diagnosis of neuropathies. It would also be interesting to examine the performance of our method on matched cohorts. Hence there should be less variation in the anatomical location where the \gls{mrn} images originate. Furthermore, an assessment of an expert in the form of an outlier-analysis could be an advisable next step to do on our \gls{mrn} images. As we showed in the first experiment, the trained neural networks mainly relied on the T2 images. However, the \gls{ir} images reduced false positive outliers and helped the network to distinguish between nerve and blood vessels. Therefore, it is crucial to further refine and optimize the \gls{mrn} sequences for even better imaging of the nerves. Both, clinicians and methods like the one we proposed would be the direct benefactors.\\
Regarding technical developments, Another point could be to reduce the axial spacing during the \gls{mrn} acquisition and reinvestigate the potential segmentation performance increase of \gls{3d} context.
Furthermore, the impact of the projection-based loss has to be examined in more detail. Perhaps more axial slices could be used to calculate the projections. Or maybe, a stack-wise 5-to-1 architecture could be expanded by two additional loss terms based on the sagittal and coronal projections. Depending on the outcome, the concept could be applied to other architectures. The fact that the projection-based neural network could almost achieve the same results speaks for it that something is going on. The projection-loss could be a way to incorporate potential anatomical shape priors into the learning phase of a neural network. We think that a combination of a neural network in conjunction with post-processing is the way to go. Post-processing, however, could be more sophisticated than ours. One could enhance our post-processing method by taking multiple paths through the graph, in order to account for the branching of the nerve. One could also change to a more sophisticated method based on a probabilistic model with anatomical constraints, similarly to~\cite{Rempfler2015ReconstructingProgramming}.
\endinput